\documentclass[11pt,letterpaper,roman]{moderncv}
\usepackage[utf8]{inputenc}

\moderncvstyle{classic}
\moderncvcolor{grey} 

\usepackage[scale=0.75]{geometry}

\geometry{letterpaper, portrait, top=1.3in, left=1.3in, bottom=1.3in, right=1.3in}

\name{David}{Lougheed}
\title{Curriculum Vitae}
\address{4830 rue Drolet app. 4}{Montréal, QC  H2L 1R1}{Canada}
\email{david.lougheed@gmail.com}
\homepage{dlougheed.com}

\begin{document}

\makecvtitle

\section{Education}
\cventry{2020 - present}{M.Sc.}{McGill University}{Montréal, QC}{}{Master's of Science, Human Genetics. Supervised by Professor Guillaume Bourque. Provisional thesis title: ``Using high-fidelity long-read sequencing to better detect and understand short tandem repeat variation in humans''. GPA: 4 out of 4.}
\cventry{2015 - 2019}{B.Sc.}{McGill University}{Montréal, QC}{}{Joint Honours, Biology and Computer Science. Honours project supervised by Professor Jérôme Waldispühl. 
Final GPA: 3.94 out of 4.}
%\cventry{2011 - 2015}{High School}{Loyalist C. V. I.}{Kingston, ON}{}{}

\section{Work Experience}
\cventry{May 2019 - August 2020}{Web Design Consultant}{Canadian Centre for Computational Genomics (C3G), McGill University}{Montréal, QC}{}
{Development of a distributed platform for the management, discovery, and analysis of genomics and other ``-omics'' data.}
\cventry{May 2018 - May 2019}{Software Development Intern}{Canadian Centre for Computational Genomics (C3G), McGill University}{Montréal, QC}{}
{Development of web applications with complex data visualization and analysis of sequencing data using bioinformatics pipelines.}
\cventry{2015 - 2017}{Developer}{Queen's University Biological Station}{Kingston, ON}{}{Development of rich content apps, complex CMS-based websites, and data processing utilities. Contracts: July-Aug. 2015, May-Aug. 2016, June-Aug. 2017.}
%\cventry{2011 - 2015}{Web Developer}{Freelance}{Kingston, ON}{}{Development of a variety of websites, ranging from static to custom CMS-powered sites.} % 2008

\section{Teaching Experience}
\cventry{Jan. 2019 - April 2019}{Teaching Assistant}{COMP 421: Database Systems}{McGill University}{}
{Responsible for holding office hours, answering student questions via email, and marking assignments and portions of a midterm exam.}
\cventry{Sept. 2016 - Dec. 2016}{TEAM Awardee}{BIOL 111: Principles: Organismal Biol.}{McGill Univ}{}
{Assisted with the lab component of the course, including answering questions and helping students follow the necessary procedures.}

\section{Recent Volunteering Experience}
\cventry{Sept. 2018 - April 2019}{Server Team Leader}{McGill Science Computer Task Force}{}{}{Organized and lead development of major web applications core to the group's
mandate. Part of the administrative council which guides the organization.}
\cventry{Dec. 2017 - Aug. 2018}{Web Team Leader}{McGill Science Computer Task Force}{}{}{Leader of a team of 12 people. Organized and led development on several projects including data visualization utilities and web applications. Part of the administrative council.}
\cventry{Feb. 2017 - Present}{Member}{McGill Science Computer Task Force}{}{}{Developed web apps, including an online election system, and administered GNU/Linux servers.}
%\cventry{Sept. 2015 - Jan. 2017}{Member}{McGill Robotics}{}{}{Led the development of a front-end interface for annotating video frames used for computer vision training.}

\section{Publications}
\cventry{2022}{Genome-wide microhomologies enable precise template-free editing of biologically relevant deletion mutations}{}{bioRxiv preprint}{}{Katherine A Aracena, Lin Y-L., Luo K., Pacis A., Gona S., Mu Z., Yotova V., Sindeaux R., Pramatarova A., Simon M-M., Chen X., Groza C., \textbf{Lougheed D.}, Grégoire R., Brownlee D., Li Y., He X., Bujold D., Pastinen T., Bourque G., Barreiro L.B. \\ DOI: \texttt{10.1101/2022.05.10.491413}}
\cventry{2020}{\textit{baRcodeR}: An open‐source R package for sample labelling}{}{Methods in Ecology and Evolution}{}{Yihan Wu, \textbf{Lougheed D.}, Lougheed S.C., Moniz K., Walker V.K., Colautti R.I.\\ DOI: \texttt{10.1111/2041-210X.13405}}
\cventry{2019}{Genome-wide microhomologies enable precise template-free editing of biologically relevant deletion mutations}{}{Nature Communications}{}{Janin Grajcarek, Monlong J.,
Nishinaka-Arai Y., Nakamura M., Nagai M., Matsuo M., \textbf{Lougheed D.}, Sakurai H., Saito M., Bourque G.\\ DOI: \texttt{10.1038/s41467-019-12829-8}}
\cventry{2018}{baRcodeR with PyTrackDat: Open-source labelling and tracking of biological samples for repeatable science}{Preprint}{bioRxiv}{}{Yihan Wu,
\textbf{Lougheed D.}, Lougheed S.C., Moniz K., Walker V.K., Colautti R.I.\\ DOI: \texttt{10.1101/457051}}

\section{Programming \& Markup Languages}
\cvitem{Python}{Proficient, especially with data processing, statistics, and web development. Experience with the Flask, Django, and Tornado web frameworks, and
with \texttt{numpy}, SKLearn, PyTorch, and Keras.}
\cvitem{JavaScript}{Proficient, including experience with NodeJS. Experience with D3 and React client-side frameworks, and the Express server-side framework.}
% \cvitem{PHP}{Proficient. Experience with Drupal and Wordpress.}
\cvitem{HTML, CSS}{Proficient, especially in modern HTML5 and CSS.}
\cvitem{C}{Experienced.} %Knowledge of Boost framework (C++).}
% \cvitem{Java}{Experienced. Some experience in Android app development.}
\cvitem{SQL}{Experienced, especially in PostgreSQL and SQLite dialects.}
\cvitem{LaTeX}{Experienced.}
\cvitem{C++}{Some experience, including with modern C++ (C++11 onwards).}
%\cvitem{R}{Some experience, mostly with data visualization.}
%\cvitem{Swift}{Some experience, specifically with iOS app development.}
\cvitem{Bash}{Some experience, mostly with server administration and basic automation.}

%\section{Other Technologies}
%\cvitem{Office Software}{Proficient with Microsoft Office and Google Docs products; some experience with LibreOffice.}
%\cvitem{Linux Server Admin.}{Experienced. Have run a VPS hosting multiple client websites since 2011.}
%\cvitem{Arduino}{Some experience. Have built and programmed small waterproof data loggers for an academic project.}

\section{Achievements}
\cventry{Feb. 2019}{Best-Designed Project}{McHacks Hackathon}{Montreal}{}{Wrote a JavaScript engine for a casual web game.}
\cventry{Feb. 2018}{Best Project Without External API Use}{McHacks Hackathon}{Montreal}{}{Wrote software for real-time signal generation and processing, used for digital 
sound synthesis, in Python using a directed-graph network.}
\cventry{Jan. 2017}{Third Place Project}{McHacks Hackathon}{Montreal}{}{Engineered a data pipeline and web application in Python and Node.JS for a neural net-powered 
Facebook chatbot.}
\cventry{Feb. 2016}{Top 10 Project}{McHacks Hackathon}{Montreal}{}{Developed a web-based chat application centred around users sending drawn messages to one another.}
%\cventry{Jun. 2014}{Bronze Medal}{Skills Canada National Competition}{Toronto}{}{Web design and development competition, both back- and front-end.}
%\cventry{May 2014}{Gold Medal}{Skills Ontario Competition}{Waterloo}{}{Web design and development competition, both back- and front-end.}

% \section{Interests}
% \cvitem{Photography}{Description}
% \cvitem{Web Dev.}{Despite often doing it as a job, I enjoy building side projects as well.}
% \cvitem{Baking}{I enjoy making bread, }

\end{document}
